Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-06-23 manuscripts/supplement.Rmd
figure tidying

\renewcommand{\thefigure}{S\arabic{figure}}
\appendix

@@

```{r Figure_S8, fig.cap="Effect of varying severity of adjustment costs on mismatches. Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g. a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.  Plots structured as in figure 7, which corresponds to the fourth panel", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") +
  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
  xlab("Penalty function")
```

@@

```{r}
source("components/vary_reduction.R")
```

Figures S9-S12 illustrate that the 
these qualitative patterns still hold at when the models are calibrated 
to a reduction in NPV of 10% or 30%, though naturally the magnitude
of the pattern is greater when the penalty is larger (e.g. 30% vs 10%).

```{r Figure_S9, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 10% reduction in NPV.  This results in a less pronounced version of the same qualitative pattern."}
p3 <- ggplot(low$dt3, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
  theme_bw() + labs(title="example trajectories at 10% reduction in NPV")

@@

```{r Figure_S10, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 30% reduction in NPV.  This results in a more pronounced version of the same qualitative pattern."}
p3 <- ggplot(high$dt3, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
  theme_bw() + labs(title="example trajectories at 30% reduction in NPV")
p3
```

```{r Figure_S11, dev=c("pdf", "svg", "png"), fig.width=5, fig.height=6, cache=FALSE, fig.cap="Identical analysis as in Figure 4 of the main text, but using a calibration to 10% reduction in NPV rather than 25%.  The qualitatively similar pattern helps illustrate that these results are not specific to the value of the reduction chosen in the main text."}
p4 <- ggplot(low$f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
  coord_cartesian(xlim = c(0, .3)) + 
  scale_color_discrete(labels=relabel, name="cost model") + 
  scale_fill_discrete(labels=relabel, name="cost model")

p4a <- p4 + 
  stat_summary(aes(y=autocorrelation),
               fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
  xlab("") + 
  labs(title="Summary statistics under a 10% reduction in NPV")

legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box")

grid.arrange(do.call(arrangeGrob, 
            lapply(list(p4a, p4b),
                   function(x) x + theme_bw() + theme(legend.position="none"))),
    legend,
    ncol = 2,
    widths = c(5,2))
```

```{r Figure_S12, dev=c("pdf", "svg", "png"), fig.width=5, fig.height=6, cache=FALSE, fig.cap="Identical analysis as in Figure 4 of the main text, but using a calibration to 30% reduction in NPV rather than 25%.  The qualitatively similar pattern helps illustrate that these results are not specific to the value of the reduction chosen in the main text."}
p4 <- ggplot(high$f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
  coord_cartesian(xlim = c(0, .3)) + 
  scale_color_discrete(labels=relabel, name="cost model") + 
  scale_fill_discrete(labels=relabel, name="cost model")

p4a <- p4 + 
  stat_summary(aes(y=autocorrelation),
               fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
  xlab("") + 
  labs(title="Summary statistics under a 30% reduction in NPV")

legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box")

grid.arrange(do.call(arrangeGrob, 
            lapply(list(p4a, p4b),
                   function(x) x + theme_bw() + theme(legend.position="none"))),
    legend,
    ncol = 2,
    widths = c(5,2))
```

>>>>

\makeatletter
\renewcommand\appendix{\par
  \setcounter{section}{0}%
  \setcounter{subsection}{0}%
  \setcounter{equation}{0}%
  \setcounter{table}{0}%------------ << add
  \setcounter{figure}{0}%----------- << add
  \gdef\theequation{S\arabic{equation}}%
  \gdef\thefigure{S\arabic{figure}}%
  \gdef\thesection{S@section}%
  \@addtoreset{equation}{section}%
  \@addtoreset{table}{section}%----- << add
  \@addtoreset{figure}{section}%---- << add
}
\makeatother

\appendix

@@

@@

```{r}
## Reset parameter values
parallel = TRUE
ncpu = parallel::detectCores()
price = 10
c0 = 30
profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
c2 <- seq(0, 40, length.out=100)
reduction <- 0.25 
seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 50               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- 0.2              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)

## Recompute
source("components/vary_reduction.R")
```

Figures S8-S11 illustrate that the 
these qualitative patterns still hold at when the models are calibrated 
to a reduction in NPV of 10% or 30%, though naturally the magnitude
of the pattern is greater when the penalty is larger (e.g. 30% vs 10%).

```{r Figure_S8, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 10% reduction in NPV.  This results in a less pronounced version of the same qualitative pattern."}
p3 <- ggplot(low$dt3, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
  theme_bw() + labs(title="example trajectories at 10% reduction in NPV")

@@

```{r Figure_S9, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 30% reduction in NPV.  This results in a more pronounced version of the same qualitative pattern."}
p3 <- ggplot(high$dt3, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
  theme_bw() + labs(title="example trajectories at 30% reduction in NPV")
p3
```

```{r Figure_S10, fig.cap="Results as in Figure 5 of the main text, but using a net reduction of NPV equal to 10%.", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}
fig5_dat <- low$dt5 %>% 
  filter(penalty_fn=="L1") %>%
  select(-penalty_fn) %>%
  unite(dist, Assumption, variable, sep = " : ")
labels <- c(expression(paste("Costs under ",  Pi[1])), 
            expression(paste("Revenue under ", Pi[1])),
            expression(paste("Cost under ", Pi[0])), 
            expression(paste("Revenue under ", Pi[0])))
ggplot(fig5_dat) + 
  geom_density(aes(value, fill=dist, color=dist, lty=dist), alpha=0.5, size=1) +
  scale_fill_discrete(name="", labels=labels) + 
  scale_color_discrete(labels=labels, name="") + 
   scale_linetype_discrete(labels=labels, name="") +
  xlab("Realized NPV") + 
  ylab("Probability density of revenue/cost")

```{r Figure_S11, fig.cap="Results as in Figure 5, but using a net reduction equal to 30%", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}
fig5_dat <- high$dt5 %>% 
  filter(penalty_fn=="L1") %>%
  select(-penalty_fn) %>%
  unite(dist, Assumption, variable, sep = " : ")
labels <- c(expression(paste("Costs under ",  Pi[1])), 
            expression(paste("Revenue under ", Pi[1])),
            expression(paste("Cost under ", Pi[0])), 
            expression(paste("Revenue under ", Pi[0])))
ggplot(fig5_dat) + 
  geom_density(aes(value, fill=dist, color=dist, lty=dist), alpha=0.5, size=1) +
  scale_fill_discrete(name="", labels=labels) + 
  scale_color_discrete(labels=labels, name="") + 
   scale_linetype_discrete(labels=labels, name="") +
  xlab("Realized NPV") + 
  ylab("Probability density of revenue/cost")

write.csv(hist_dat, "components/data/figure5.csv")
```
